---
title: "RRWM"
author: "Chris Borst"
date: "2023-09-22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Reproducible Research and Workflow Management Data Activity

Knitting this RMarkdown document will reproduce all results generated.

**NOTE: FIRST MANUALLY CHANGE THE FILE PATH IN config.R TO YOUR DESIRED WORKING DIRECTORY**
Because the raw data cannot be shared, the scripts assume that the raw data is located in 
the **parent** directory of the working directory.

I am not confident that the package bundler has worked as intended. I tried checkpoint first, but
it threw an error, suggesting that not all the packages used were available at the checkpoint.
This uses renv. Everything *looks* right, but when I render it says there's no lockfile. But the
lockfile is _right there_. If this throws an error for you, open config.R and delete the first line.
Everything else works.

```{r config}
source(here::here("code","config.R"))
```


```{r data_cleaning}
source(here::here("code","GSS_Data_Cleaning.R"))
```


```{r tables}
source(here::here("code","Basic_tables.R"))
```


```{r model}
source(here::here("code","Model.R"))
```


```{r results}
source(here::here("code","Results_tables.R"))
```

