---
title: "RRWM"
author: "Chris Borst"
date: "2023-09-22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_knit$set(root.dir = "/Users/chrisborst/Desktop/CAnD3/RRWM/CAND3 Data/GSS 2017 - Family, Cycle 31/Repro_Project")
```

## Reproducible Research and Workflow Management Data Activity

Knitting this RMarkdown document will reproduce all results generated.

**NOTE: FIRST MANUALLY CHANGE THE FILE PATH IN THE ABOVE CODE CHUNK TO YOUR DESIRED WORKING DIRECTORY**

Also note that, because the raw data cannot be shared, the scripts assume that the raw data is located in 
the **parent** directory of the working directory.


```{r config}
source(here::here("code","config.R"))
```


```{r data_cleaning}
source(here::here("code","GSS_Data_Cleaning.R"))
```


```{r tables}
source(here::here("code","Basic_tables.R"))
```


```{r model}
source(here::here("code","Model.R"))
```


```{r results}
source(here::here("code","Results_tables.R"))
```

